Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
app
tex

\section{More Technical Details}

In this section, we provide more details on the reasons of our design,
additional details of our implementation, as well as more discussions
on questions that are unsuitable for the main part of manuscript.

@@

	\item Details of EST?

	\item Details of ACT?
%
Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.
%
However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.

@@

	\item [?] Can we learn more from the third and fourth standard moments?
		Namely skewness and kurtosis.

	\item [M] manuscript notes on LGA.

@@

	\item [GA] Also scale the $H_D-H_S$ part?
		(1) $$ H_\mathsf{GA} \leftarrow (H_\mathsf{D} + U - H_\mathsf{S}) * nL $$
		(2) $$ H_\mathsf{GA} \leftarrow H_\mathsf{D} + U * nL $$
		(3) pure GA for ablation $$ H_\mathsf{GA} \leftarrow U * nL $$
		interpret with lessons learned from HM matrix.

	\item [ICS] Adversarial training (does not allow any distance moving) may
		encourage collapse (a trivial solution to the requirement). What if we
		loosen the requirement and convert it into a new constraint? For
		instance, \[
			L=L_{base}(a,p,n)+\lambda_{1}L(a,\tilde{a},p)+\lambda_{2}L_{triplet}(a,\tilde{a},n)
		\] where the $L_{base}$ can be either $L_{triplet}$, $L_{rest}$, or
		$L_{act}$. Question: should we do this for every sample? i.e., \[
			L_{loosen}(a,p,n)=L_{base}(a,p,n)+\sum_{x\in\{a,p,n\}}L(x,\tilde{x},n_{x})
		\]

>>>>

\section{More Technical and Design Details}

\noindent\textbf{I. Hardware and Software Platform.}

We conduct the experiments with two Nvidia Titan Xp GPUs under the Ubuntu 16.04
operating system with PyTorch 1.8.2 in distributed data parallel mode.

\noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}

Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterparts
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, and $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
The $\tilde{\vp}$ and $\tilde{\vn}$ are obtained similarly.

\ul{Relationship with HM:}
%
Since EST only aims to maximize the embedding move distance off its original
location without specifying any direction, it leads to a random hardness
value.
%
Because the perturbed triplet can be either harder or easier than the benign
triplet.
%
Namely, EST merely indirectly increase the hardness of the training
triplet, and may even decrease its hardness.
%
Thus, EST suffers from inefficiency in adversarial training compared to HM.

\noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}

Anti-Collapse Triplet (ACT)~\cite{robrank} ``collapses'' the embedding vectors
of positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.

\ul{Relationship with HM:}

\oo{todo}

However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.

@@

@@

@@
